---
title: "R-ex"
author: "Hill"
date: "2/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Wildfire (60 points)
Australia is currently in the midst of the [worst wildfire season in recent
memory](https://www.cnn.com/2020/01/01/australia/australia-fires-explainer-intl-hnk-scli/index.html).
At least two dozen people have been killed. Over 12 million acres of land have
been burned and an estimated 480 million animals have died^[[Using US map to
examine scale of massive Australia
wildfires](https://abcnews.go.com/International/us-map-examine-scale-massive-australia-wildfires/story?id=68102703)].
The impact has been catastrophic.

Fires are exceptionally difficult to predict. [Wildfire
modeling](https://en.wikipedia.org/wiki/Wildfire_modeling) is typically based on
simulation and is often complex and difficult. However, we can create a
simplified wildfire simulation with the following guidelines:

* Start with a known number of trees burning
* For each burning tree, there are a random number of trees (defined by a
geometric distribution with `prob = 0.5`) within the "danger zone"
* Each tree within the "danger zone" has a fixed probability of catching on fire
* As each new tree catches fire, the cycle repeats

This process can be conceptually represented as a two step cycle:
1. How many trees are currently in the "danger zone"
2. How many of the trees in the "danger zone" actually catch fire. This number
becomes the next input for determining step 1.

Given this simplified approach, there are two possible simulation outcomes:
Either the fire dies out or it consumes the entire forest.

Helpful hints:
* You can draw random values from the geometric distribution with the `rgeom()`
function

1. (35 points) Define a function called `wildfire` that simulates a single
scenario. This function should take 3 arguments:
  * `p`: the likelihood that a tree in the "danger zone" catches fire
  * `burning`: the number of trees initially burning
  * `total_trees`: the total number of trees in the forest  
This function should return the total number of trees burned.

```{r}

wildfire <- function(p, burning, total_trees) {
  #we will have to use the remaining tree count to find the total
  remain_tree <- total_trees - burning
  #initial burning tree is the initial count of burnt trees
  burnt_trees <- burning
  
  for (i in 1:length(burning)) {
    burning <- burning[i]
    danger_zone <-  sum(rgeom(burning, prob = 0.5))
    while (remain_tree > 0) {
      if (danger_zone == 0) {
        break
      }
      if (remain_tree < danger_zone) {
        remain_tree = danger_zone
      }
      else if (danger_zone > 0) {
        burning <-
          sum(replicate(danger_zone, sample(c(0, 1), 1, prob = c(1 - p, p))))
        burnt_trees <- burnt_trees + burning
        remain_tree <- remain_tree - danger_zone
      }
    }
  }
  return(burnt_trees)
}

```


2. (10 points) Using the function defined in step 1, run this simulation 10,000
times each for the following two scenarios:
  * Fire starts with 1 burning tree, `p = 0.9`, with 1,000 trees in the forest
  * Fire starts with 6 burning trees, `p = 0.4`, with 1,000 trees in the forest

```{r}
#the for loop I used makes this run pretty slow...

n_sims <- 10000

one_tree <-
  replicate(n_sims, wildfire(
    p = 0.9,
    burning = 1,
    total_trees = 1000
  ))
six_tree <-
  replicate(n_sims, wildfire(
    p = 0.4,
    burning = 6,
    total_trees =  1000
  ))

```

3. (10 points) Using the results from step 2, estimate the average number of
trees burned in each scenario.
```{r}
mean(one_tree)
mean(six_tree)
```

4. (5 points) Calculate a 95% confidence interval for the two estimates
calculated in step 3.
```{r}
CInt <- function(x, alpha = 0.05) {
  n <- length(x)
  est <- mean(x)
  sd <- sd(x)
  CInt <- est + c(-1, 1) * qnorm(1 - (alpha / 2)) * sd / sqrt(n)
  c(lower = CInt[1],
    est = est,
    upper = CInt[2])
}
CInt(one_tree)
CInt(six_tree)
```

## Utah Jazz (45 points)
The Utah Jazz are in the midst of an impressive season. At the time of writing
this question (2020-01-18) the Jazz have a 29-13 record (29 wins, 13 losses).
This translates to a win percentage of .690 (29 / (29 + 13)) The file
`opponents.csv` contains Jazz opponents for the remainder of the season and
their current win-loss record. Please note the in the course of a season, the
Jazz play teams multiple times, so it is expected to see teams repeated on the
schedule.

Given a game between two opponents (referred to as A and B), the likelihood that
team A wins is defined as^[[Probabilities of Victory in Head-to-Head Team
Matchups](https://sabr.org/research/probabilities-victory-head-head-team-matchups)]:

$$
P_A = \frac{WP_A(1 - WP_B)}{WP_A(1 - WP_B) + WP_B(1 - WP_A)}
$$

Where $P_A$ is the probability that team A wins, $WP_A$ is the winning
percentage of team A, and $WP_B$ is the winning percentage of team B.

Using this equation, create a function that simulates the remainder of the Jazz
season by estimating the outcome of each remaining game. This simulation should
use the Jazz's current win percentage as the Jazz's win percentage for every
game (in other words, you don't need to use the previously simulated game to
adjust the Jazz's win percentage).

1. (30 points) Define a function called `jazz`  that simulates the remainder of
the Jazz's season. This function should return the total number of wins the Jazz
have at the end of the season.

```{r}
Jazz <- function() {
  Win <- 29
  jazz_sched <-
    read.csv("jazz-schedule.csv", header = TRUE, sep = ",")
  WP_A <- .69
  jazz_sched$percentages <-
    jazz_sched$wins / (jazz_sched$wins + jazz_sched$losses)
  for (i in 1:length(jazz_sched$percentages)) {
    WP_B <- jazz_sched$percentages[i]
    win_prob <-
      {
        WP_A * (1 - WP_B)
      } / {
        (WP_A * (1 - WP_B) + WP_B * (1 - WP_A))
      }
    result <- sample(c(0, 1), 1, prob = c((1 - win_prob), win_prob))
    if (result == 1) {
      Win <- Win + 1
    }
  }
  return(Win)
}

```


2. (5 points) Using the function defined in 1, run this simulation 10,000 times and store the results.
```{r}
n_reps <- 10000

super_jazz <- replicate(n_reps, Jazz())
```

3. (5 points) Using the results from step 2, estimate the likelihood that the
Jazz win at least 60 games this season.

```{r}
sixty_prob <- mean(super_jazz >= 60)

```

4. (5 points) Calculate a 95% confidence interval on the estimate from the
previous step.

```{r}
ci <-
  sixty_prob + c(-1, 1) * qnorm(0.975) * sqrt(sixty_prob * (1 - sixty_prob) / length(super_jazz))
c(lower = ci[1],
  sixty_prob = sixty_prob,
  upper = ci[2])


```

