---
title: "showers"
author: "Hill"
date: "2/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Showers

You think that your roommate takes showers whose duration is different from
yours. Your roommate disagrees but, instead of arguing, you both decide to keep
track of the time it takes both of you to shower for fourteen days and then to
employ skills from an introductory statistics class (e.g., STAT 121) to create a
confidence interval on the population mean showering time of your roommate minus
the population mean showering time of you. The data and code to compute a 90%
confidence interval are below.

```{r}
roommate <- c(6,6.25,5.75,6.5,6,15,35,20,4,5.25,5.75)

you <- c(3.5,5.5,4,4,4,6,11,12,3,4,4.25,7,3.25)

t.test(roommate, you, conf.level = 0.9)
```


Notice that the confidence interval contains 0 and, therefore, your roommate
concludes that there is no significant difference in the time it takes you
both to take a shower. But it might be inappropriate to use this confidence
interval on the difference in means because the data are not normally
distributed and the sample sizes are small. 

+ Use the bootstrap procedure to compute a 90% confidence interval on the
difference in these means. 

Based on this bootstrap confidence interval, what
conclusion do you make at the 0.10 level of significance?
#I would conclude that we are able to reject the null hypothesis as our interval does not include zero 


```{r}
n_samples <- 10000
shower_differences <- replicate(n_samples, mean(sample(roommate, replace = TRUE)) - mean(sample(you, replace = TRUE)))

ci <- quantile(shower_differences, probs = c(0.025, 0.975), CI.level = .90)
ci

```

Based on this bootstrap confidence interval, what
conclusion do you make at the 0.10 level of significance?
#I would conclude that we are able to reject the null hypothesis as our interval does not include zero as such the mean difference is not equal to zero. 


```{r}
#JUSTFORFUN(and practice)
plot(density(shower_differences))
abline(v = ci, col = "blue")
```


