---
title: "Trees bootstrapping"
author: "Hill"
date: "2/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Trees
 
In the trees dataset found in R, there are three variables "Girth" "Height"
and "Volume". There is interest in using "Girth" and "Height"(two noninvasive
measures) to predict "Volume". Carrying out this prediction can be done using a
regression model with two explanatory variables ("Height" and "Girth"). This
model can very easily be fit in R using the following two lines of code.
```{r}

data(trees)
  
lm(Volume ~ Height + Girth, data=trees)


```


```{r}
treefun<-function(){
samp_tree <- sample(1:nrow(trees), nrow(trees), replace = TRUE)
xtree <- trees[samp_tree,]

modelthing<-lm(Volume ~ Height + Girth, data=xtree)
coef(modelthing)[2]/coef(modelthing)[3]
}
```

Principal interest lies in estimating the regression coefficient of "Height"
divided by the regression coefficient for "Girth". Obtaining a estimate of
the ratio is easy --- just compute the ratio of the two slope estimates ---
but assessing uncertainty associated with the point estimate can be
difficult theoretically (although methods do exist). 

+ For this problem construct an 95% confidence interval using the bootstrap 
procedure. Use 5,000 bootstrap samples.
```{r}
n_samples<- 5000

tree_strap<-replicate(n_samples, mean(treefun()))
mean(tree_strap)

ci <- quantile(tree_strap, probs = c(0.025, 0.975))

```
